### 2021-02-26 yfcc100m/paper/vldb2021/design.tex
Minor updates to design

VDMS API provides mechanism to insert and connect Images, Videos, BoundingBoxes,
Frames, and Descriptors (feature vectors), together with any metadata
associated with the objects.
Each object is a node in the graph.
The metadata associated to each object is is modeled as
"properties" of the node in the graph.
Users can query, filter, and retrieve this objects based
on its metadata (the "properties" associated with them).
VDMS does not simply treat these objects as binary blobs of data, but rather
understands them and the type of processing that is common for them,
providing the ability to run processing on-the-fly, both at insertion and
at retrieval type.
Users can, for instance, retrieve a resized version of an image,
or retrieve only a clip from a large video.
This is one of the main differentiation aspect when compared to other
database systems, including relational databases.
In a relational database, for instance, one can query \textit{and compute}
over values in a column only for basic data types (strings, integers, floats),
and over the abstractions the relational model support (tables, columns).
A SQL query can then retrieve the \textit{computed average} "salary" of all
the employees in a company (stored using the table/columns abstraction),
but cannot perform any computation over data stored as a blob or binary object.
VDMS, because it recognized the nature of visual objects by design,
provides the ability to \textit{compute} on these visual objects
(image, videos, etc).

@@

The Graph Engine used for in VDMS is the
\textit{Persistent Memory Graph Database} (PMGD).
PMGD was developed at Intel Labs, and was designed and optimized for
persistent memory technologies like Intel Optane~\cite{IntelXPoint15}, which
promise storage providing nearly the speed of DRAM and the
durability of block-oriented storage.
PMGD is also fully open-sourced \footnote{https://github.com/IntelLabs/pmgd}.
PMGD implements an in-persistent-memory graph database, PMGD, optimized
to run on a platform equipped with persistent memory, but
also provides the option to run on SSD and ext4 filesystem
using OS support to provide transactional guarantees (through \textit{msync}).
PMGD provides a property graph model of data storage with the traditional
atomicity, consistency, isolation, and durability
(ACID) properties expected from databases.
PMGD comes as a C++ library that VDMS uses for its internal query engine.
Because PMGD already supports most of the graph abstractions we wanted
to see on VDMS API, it was our preferred option.
Also, our internal evaluation shows that PMGD is faster
than other graph databases, including Neo4j\cite{miller2013graph}.
PMGD performance evaluation will be published separately.

@@

The client library implements TCP/IP based connectors to the VDMS Server,
similar to most database\cite{memsql, mysql, postgresql}.
Users can connect to VDMS and implement queries using VDMS' API
by defining JSON commands conforming to the query protocol we have defined.
The client library provides a simple method that
accepts a JSON string and an array or vector of blobs.
Internally, the library wraps the query string and blobs using
Google Protobufs \cite{protobufs} and sends it to the VDMS server.
It also receives a similarly formed response from VDMS
and returns it to the client.
The responses require JSON parsing on the client
side for the metadata string that indicates how to interpret the blobs field.
Currently, client libraries are implemented for Python and C++ client.
The client libraries are lightweight, as they simply implement the communication
protocol between the client and the server.
This makes it easier for developers to implement similar client libraries using
any other programming language of their choice.

>>>>

VDMS API provides a mechanism to insert and connect Images, Videos, BoundingBoxes,
Frames, and Descriptors (feature vectors), together with any metadata
associated with the objects.
Each object is a node in the graph.
The metadata associated to each object is modeled as
"properties" of the node in the graph.
Users can query, filter, and retrieve this objects based
on its metadata (the "properties" associated with them).
VDMS does not simply treat these objects as binary blobs of data, but rather
understands them and the type of processing that is common for them,
providing the ability to run processing on-the-fly, both at insertion and
retrieval.
Users can, for instance, retrieve a resized version of an image,
or retrieve only a clip from a large video.
This is one of the main differentiation aspect when compared to other
database systems, including relational databases.
In a relational database, for instance, one can query \textit{and compute}
over values in a column only for basic data types (strings, integers, floats),
and over the abstractions the relational model supports (tables, columns).
A SQL query can then retrieve the \textit{computed average} "salary" of all
the employees in a company (stored using the table/columns abstraction),
but cannot perform any computation over data stored as a blob or binary object.
VDMS, because it recognized the nature of visual objects by design,
provides the ability to \textit{compute} on these visual objects
(image, videos, etc).

@@

The Graph Engine used in VDMS is the
\textit{Persistent Memory Graph Database} (PMGD).
PMGD was developed at Intel Labs, and was designed and optimized for
persistent memory technologies like Intel Optane~\cite{IntelXPoint15}, which
promise storage providing nearly the speed of DRAM and the
durability of block-oriented storage.
PMGD is also fully open-sourced \footnote{https://github.com/IntelLabs/pmgd}.
PMGD implements an in-persistent-memory graph database, PMGD, optimized
to run on a platform equipped with persistent memory, but
also provides the option to run on SSD and ext4 filesystem
using OS support to provide transactional guarantees (through \textit{msync}).
PMGD provides a property graph model of data storage with the traditional
atomicity, consistency, isolation, and durability
(ACID) properties expected from databases.
PMGD comes as a C++ library that VDMS uses for its internal query engine.
Because PMGD already supports most of the graph abstractions we wanted
to see on VDMS API, it was our preferred option.
Also, our internal evaluation shows that PMGD is faster
than other graph databases, including Neo4j\cite{miller2013graph}.
PMGD performance evaluation will be published separately.

@@

The client library implements TCP/IP based connectors to the VDMS Server,
similar to most databases\cite{memsql, mysql, postgresql}.
Users can connect to VDMS and implement queries using VDMS' API
by defining JSON commands conforming to the query protocol we have defined.
The client library provides a simple method that
accepts a JSON string and an array or vector of blobs.
Internally, the library wraps the query string and blobs using
Google Protobufs \cite{protobufs} and sends it to the VDMS server.
It also receives a similarly formed response from VDMS
and returns it to the client.
The responses require JSON parsing on the client
side for the metadata string that indicates how to interpret the blobs field.
Currently, client libraries are implemented for Python and C++ client.
The client libraries are lightweight, as they simply implement the communication
protocol between the client and the server.
This makes it easier for developers to implement similar client libraries using
any other programming language of their choice.
